Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-06-01 draft.tex
fix statement about infinite horizon
modify figure 1

The game is infinitely repeated and proceeds as follows. At the beginning of each period, the payoffs for the secessionists from unrecognized statehood---to which we refer as the status quo---deteriorate by a fixed amount, representing the ongoing costs of non-recognition. Next, the patron and international community can, in turn, make investments to augment the payoffs of the home state government and the secessionists. Finally, the home government and secessionists play a simultaneous stage game in which each decides whether to initiate conflict, maintain the status quo of unrecognized statehood, or cede the issue of status.

@@

Although we are not aware of any formal models of unrecognized statehood there is a growing economics literature that employs game theoretic models of conflict. Grossman (2004) offers an early model of territorial disputes in which the divisibility of the contested territory is an important parameter. In Hirschleifer, Boldrin and Levin (2009), conflict can be avoided when there is common knowledge, a common rate of time preference, and players can make a series of small concessions. In our context, the contested territory is indivisible; this implies that peace would require very large concessions so that this pathway of using small compromises to avoid conflict is not available.

@@

\subsection{Timing and Structure of Interaction}
\label{sec:structure}

>>>>

The dynamic game has an infinite horizon and proceeds as follows. At the beginning of each period, the payoffs for the secessionists from unrecognized statehood---to which we refer as the status quo---deteriorate by a fixed amount, representing the ongoing costs of non-recognition. Next, the patron and international community can, in turn, make investments to augment the payoffs of the home state government and the secessionists. Finally, the home government and secessionists play a simultaneous stage game in which each decides whether to initiate conflict, maintain the status quo of unrecognized statehood, or cede the issue of status.

@@

Although we are not aware of any formal models of unrecognized statehood there is a growing economics literature that employs game theoretic models of conflict. Grossman (2004) offers an early model of territorial disputes in which the divisibility of the contested territory is an important parameter. In Hirshleifer, Boldrin and Levin (2009), conflict can be avoided when there is common knowledge, a common rate of time preference, and players can make a series of small concessions. In our context, the contested territory is indivisible; this implies that peace would require very large concessions so that this pathway of using small compromises to avoid conflict is not available.

@@

\subsection{Interaction within a Period}
\label{sec:structure}
